Phenology and Mycorrhizae Manuscript

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
Add windspeed

>>>>

#Download Windspeed
```{r}
dataName="NEON_Windspeed"
NEON_ID='DP1.00001.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
# inFileName <- "PARPAR_30min.csv"
# varName <- "PARMean"
